---
title: "Multiple Regression"
author: Josh Jackson
date: "10-20-20"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
mono_light(
  base_color = "#23395b",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono"),
)




library(tidyverse)
library(broom)
```



```{css, echo=FALSE}
pre, code {white-space:pre !important; overflow-x:auto}
```



<style type="text/css">
.remark-slide-content {
    font-size: 30px;
    padding: 1em 4em 1em 4em;
}

.small .remark-code { 
  font-size: 80% !important;
}
.tiny .remark-code {
  font-size: 65% !important;
}
</style>





## This time
Incorporate more than 1 predictor  
Visualize marginal effects  
Categorical predictors with >2 levels


---

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(patchwork)
library(tidyverse)

# normal density
p1 <-
  tibble(x = seq(from = -3, to = 3, by = .1)) %>% 
  ggplot(aes(x = x, ymin = 0, ymax = (dnorm(x)) / max(dnorm(x)))) +
  geom_ribbon(fill = "steelblue4", color = "steelblue4", alpha = .6) +
  annotate(geom = "text",
           x = 0, y = .2,
           label = "normal",
           size = 7) +
  annotate(geom = "text",
           x = c(0, 1.5), y = .6,
           label = c("italic(M)[0]", "italic(S)[0]"), 
           size = 7, family = "Times", parse = T) +
  scale_x_continuous(expand = c(0, 0)) +
  theme_void() +
  theme(axis.line.x = element_line(size = 0.5))

# a second normal density
p2 <-
  tibble(x = seq(from = -3, to = 3, by = .1)) %>% 
  ggplot(aes(x = x, ymin = 0, ymax = (dnorm(x)) / max(dnorm(x)))) +
  geom_ribbon(fill = "steelblue4", color = "steelblue4", alpha = .6) +
  annotate(geom = "text",
           x = 0, y = .2,
           label = "normal",
           size = 7) +
  annotate(geom = "text",
           x = c(0, 1.5), y = .6,
           label = c("italic(M)[italic(j)]", "italic(S)[italic(j)]"), 
           size = 7, family = "Times", parse = T) +
  scale_x_continuous(expand = c(0, 0)) +
  theme_void() +
  theme(axis.line.x = element_line(size = 0.5))

## two annotated arrows
# save our custom arrow settings
my_arrow <- arrow(angle = 20, length = unit(0.35, "cm"), type = "closed")
p3 <-
  tibble(x    = c(.33, 1.67),
         y    = c(1, 1),
         xend = c(.67, 1.2),
         yend = c(0, 0)) %>%
  
  ggplot(aes(x = x, xend = xend,
             y = y, yend = yend)) +
  geom_segment(arrow = my_arrow) +
  annotate(geom = "text",
  x = c(.35, 1.3), y = .5,
  label = "'~'",
  size = 10, family = "Times", parse = T) +
  xlim(0, 2) +
  theme_void()

# exponential density
p4 <-
  tibble(x = seq(from = 0, to = 1, by = .01)) %>% 
  ggplot(aes(x = x, ymin = 0, ymax = (dexp(x, 2) / max(dexp(x, 2))))) +
  geom_ribbon(fill = "steelblue4", color = "steelblue4", alpha = .6) +
  annotate(geom = "text",
           x = .5, y = .2,
           label = "exp",
           size = 7) +
  annotate(geom = "text",
           x = .5, y = .6,
           label = "italic(K)",
           size = 7, family = "Times", parse = T) +
  scale_x_continuous(expand = c(0, 0)) +
  theme_void() +
  theme(axis.line.x = element_line(size = 0.5))

# likelihood formula
p5 <-
  tibble(x = .5,
         y = .25,
         label = "beta[0]+sum()[italic(j)]*beta[italic(j)]*italic(x)[italic(ji)]") %>% 
  
  ggplot(aes(x = x, y = y, label = label)) +
  geom_text(size = 7, parse = T, family = "Times") +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1)) +
  ylim(0, 1) +
  theme_void()
  
  # half-normal density
p6 <-
  tibble(x = seq(from = 0, to = 3, by = .01)) %>% 
  ggplot(aes(x = x, ymin = 0, ymax = (dnorm(x)) / max(dnorm(x)))) +
  geom_ribbon(fill = "steelblue4", color = "steelblue4", alpha = .6) +
  annotate(geom = "text",
           x = 1.5, y = .2,
           label = "half-normal",
           size = 7) +
  annotate(geom = "text",
           x = 1.5, y = .6,
           label = "0*','*~italic(S)[sigma]", 
           size = 7, family = "Times", parse = T) +
  scale_x_continuous(expand = c(0, 0)) +
  theme_void() +
  theme(axis.line.x = element_line(size = 0.5))

# three annotated arrows
p7 <-
  tibble(x    = c( .43, 1.5, 2.5),
         y    = c( 1, 1, 1),
         xend = c( 1.225, 1.5, 1.75),
         yend = c( .15, .2, .2)) %>%
  
  ggplot(aes(x = x, xend = xend,
             y = y, yend = yend)) +
  geom_segment(arrow = my_arrow) +
  annotate(geom = "text",
           x = c( .7, 1.38, 2), y = c( .22, .65, .6),
           label = c( "'~'", "'='", "'~'"),
           size = 10, family = "Times", parse = T) +
  #annotate(geom = "text",
          # x = .43, y = .7,
           #label = "nu*minute+1",
           #size = 7, family = "Times", parse = T) +
  xlim(0, 3) +
  theme_void()

# student-t density
p8 <-
  tibble(x = seq(from = -3, to = 3, by = .1)) %>% 
  ggplot(aes(x = x, ymin = 0, ymax = (dt(x, 3) / max(dt(x, 3))))) +
  geom_ribbon(fill = "steelblue4", color = "steelblue4", alpha = .6) +
  annotate(geom = "text",
           x = 0, y = .2,
           label = "student t",
           size = 7) +
  annotate(geom = "text",
           x = 0, y = .6,
           label = "nu~~~mu[italic(i)]~~~sigma",
           size = 7, family = "Times", parse = T) +
  scale_x_continuous(expand = c(0, 0)) +
  theme_void() +
  theme(axis.line.x = element_line(size = 0.5))

# the final annotated arrow
p9 <-
  tibble(x     = c(.375, .625),
         y     = c(1/3, 1/3),
         label = c("'~'", "italic(i)")) %>%

  ggplot(aes(x = x, y = y, label = label)) +
  geom_text(size = c(10, 7), parse = T, family = "Times") +
  geom_segment(x = .5, xend = .5,
               y = 1, yend = 0,
               arrow = my_arrow) +
  xlim(0, 1) +
  theme_void()

# some text
p10 <-
  tibble(x     = .5,
         y     = .5,
         label = "italic(y[i])") %>% 
  
  ggplot(aes(x = x, y = y, label = label)) +
  geom_text(size = 7, parse = T, family = "Times") +
  xlim(0, 1) +
  theme_void()

# define the layout
layout <- c(
  area(t = 1, b = 2, l = 3, r = 5),
  area(t = 1, b = 2, l = 7, r = 9),
  area(t = 4, b = 5, l = 1, r = 3),
  area(t = 4, b = 5, l = 5, r = 7),
  area(t = 4, b = 5, l = 9, r = 11),
  area(t = 3, b = 4, l = 3, r = 9),
  area(t = 7, b = 8, l = 5, r = 7),
  area(t = 6, b = 7, l = 1, r = 11),
  area(t = 9, b = 9, l = 5, r = 7),
  area(t = 10, b = 10, l = 5, r = 7)
)

# combine and plot!
(p1 + p2 + p4 + p5 + p6 + p3 + p8 + p7 + p9 + p10) + 
  plot_layout(design = layout) &
  ylim(0, 1) &
  theme(plot.margin = margin(0, 5.5, 0, 5.5))
```


---

Can you write this model equation? Assume two IVs. 


---
## data 


```{r, message = FALSE}
MR <- MR %>% 
  mutate(SS_c = `schoool success` - mean(`schoool success`),
         FQ_c = `friendship quality` - mean(`friendship quality`),
         iv = `intervention group`,
         iv.d = recode(`iv`, 
                             `1` = "control", 
                             `2` = "tx", 
                             `3` = "tx"),
         iv.d = factor(iv.d))

MR
```

---

```{r, message=FALSE}
library(psych)
describe(MR)
```




---
## model 

happiness ~ Normal( $\mu_i$ , $\sigma$ )  

$\mu_i$ = $\beta_0$ + $\beta_1$ $SS\_c$ + $\beta_2$ $FQ\_c$     

$\beta_0$ ~ Normal(0, 5)   
$\beta_1$ ~ Normal(0, 5)   
$\beta_2$ ~ Normal(0, 5)   
$\sigma$  ~ HalfCauchy(0,10) 

---

```{r, message=FALSE}
library(brms)
mr.1 <- 
  brm(family = gaussian,
      happiness ~ 1 + SS_c + FQ_c,
      prior = c(prior(normal(5, 2), class = Intercept),
                prior(normal(0, 2), class = b, coef = SS_c),
                prior(normal(0, 2), class = b, coef = FQ_c),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = MR,
      sample_prior = T,
      file = "mr.1")
```

---

equivalent notation
```{r, eval=FALSE}

library(brms)
mr.1 <- 
  brm(family = gaussian,
      happiness ~ 1 + SS_c + FQ_c,
      prior = c(prior(normal(5, 2), class = Intercept),
                prior(normal(0, 2), class = b),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = MR,
      sample_prior = T,
      file = "mr.1")

```



---

```{r}
prior.mr1<- prior_draws(mr.1)
prior.mr1
```


---
## Prior predictive checks

.pull-left[
```{r, eval = FALSE}
prior.mr1 %>% 
  sample_n(size = 100) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, Intercept, b_SS_c),
         a = c(-10, 10)) %>% 
  mutate(d = Intercept + b_SS_c * a) %>% 
  
  ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw), alpha = .4) +
  labs(x = "Centered School Success",
       y = "happiness") +
  coord_cartesian(ylim = c(0, 10)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 
```
]

.pull-right[

```{r, echo = FALSE}
prior.mr1 %>% 
  sample_n(size = 100) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, Intercept, b_SS_c),
         a = c(-10, 10)) %>% 
  mutate(d = Intercept + b_SS_c * a) %>% 
  
  ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw), alpha = .4) +
  labs(x = "Centered School Success",
       y = "happiness") +
  coord_cartesian(ylim = c(0, 10)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 
```



]

---
### tighter priors? 

```{r}
mr.2 <- 
  brm(family = gaussian,
      happiness ~ 1 + SS_c + FQ_c,
      prior = c(prior(normal(5, 2), class = Intercept),
                prior(normal(0, .2), class = b, coef = SS_c),
                prior(normal(0, .2), class = b, coef = FQ_c),
                prior(exponential(.5), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = MR,
      sample_prior = T,
      file = "mr.2")
```


---

```{r, echo = FALSE}
prior.mr2<- prior_samples(mr.2)
prior.mr2 %>% 
  sample_n(size = 100) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, Intercept, b_SS_c),
         a = c(-10, 10)) %>% 
  mutate(d = Intercept + b_SS_c * a) %>% 
  
  ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw), alpha = .4) +
  labs(x = "Centered School Success",
       y = "happiness") +
  coord_cartesian(ylim = c(0, 10)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 
```


---

```{r}
summary(mr.1)
## weak/non-informative prior model
```


---

```{r}
summary(mr.2)
## modestly informative prior model
```


---

```{r}
plot(mr.1)
```

---

```{r}
conditional_effects(mr.1)
```

---
## Conditional plots 
.pull-left[
SS_c first

```{r, message=FALSE, warning=FALSE, eval=FALSE}
library(tidybayes)
library(modelr)

MR %>% 
  data_grid(SS_c = seq_range(SS_c, n = 101), .model=MR) %>%
 add_epred_draws(mr.1) %>% 
  ggplot(aes(x = SS_c, y = happiness)) +
  stat_lineribbon(aes(y = .epred), .width = c(.95), color = "grey") + geom_point(data = MR, size = 2)  
  
```
]

.pull-right[

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(tidybayes)
library(modelr)
MR %>% 
  data_grid(SS_c = seq_range(SS_c, n = 101), .model=MR) %>%
 add_epred_draws(mr.1) %>% 
  ggplot(aes(x = SS_c, y = happiness)) +
  stat_lineribbon(aes(y = .epred), .width = c(.95), color = "grey") + geom_point(data = MR, size = 2)  
  
```

]

---
FQ_c
```{r, echo = FALSE}
MR %>% 
  data_grid(FQ_c = seq_range(FQ_c, n = 101), .model=MR) %>%
 add_epred_draws(mr.1) %>% 
  ggplot(aes(x = FQ_c, y = happiness)) +
  stat_lineribbon(aes(y = .epred), .width = c(.95), color = "grey") + geom_point(data = MR, size = 2)  
  
```


---

```{r}
get_variables(mr.1)
```



```{r}
head(mr.1 %>% 
spread_draws(b_Intercept, b_SS_c, b_FQ_c, sigma))
```


---
```{r, options(width=150)}
head(MR %>% 
 add_epred_draws(mr.1))
```
236,000 rows comes from (N = 118 * 2000 post warmup samples). Different .epred (y-hat, expected/fitted value) for each person for each sample. 

---

```{r}
MR %>% 
  data_grid(FQ_c = seq_range(FQ_c, n = 101), .model=MR)
```


---

```{r}
MR %>% 
  data_grid(FQ_c, .model = MR) %>% 
  add_predicted_draws(mr.1) %>% 
    ggplot(aes(x = FQ_c, y = happiness)) +
  stat_lineribbon(aes(y = .prediction), .width = c(.95), color = "grey") + geom_point(data = MR, size = 2) 
```

FQ_c has 101 different values, ranging from min to max. Everything else is set at "typical" values. ]

---

```{r}
MR %>% 
  data_grid(FQ_c = seq_range(FQ_c, n = 101), .model=MR) %>%
 add_epred_draws(mr.1)
```
We feed the 101 FQ_c values (and the constant other values) into our posterior, which has different intercept and regression values for each of the 2000 samples. 202,000 = 101 * 2000 


---
## Fitted values at different levels of the other variable

.pull-left[
```{r, eval = FALSE}
MR %>% 
  data_grid(SS_c = seq_range(SS_c, n = 101), FQ_c = -7, .model=MR) %>%
 add_epred_draws(mr.1) %>% 
  ggplot(aes(x = SS_c, y = happiness)) +
  stat_lineribbon(aes(y = .epred), .width = c(.95), color = "grey") + geom_point(data = MR, size = 2)  
```

]

.pull-right[
```{r, echo = FALSE}
MR %>% 
  data_grid(SS_c = seq_range(SS_c, n = 101), FQ_c = -7, .model=MR) %>%
 add_epred_draws(mr.1) %>% 
  ggplot(aes(x = SS_c, y = happiness)) +
  stat_lineribbon(aes(y = .epred), .width = c(.95), color = "grey") + geom_point(data = MR, size = 2)  
```
]



---
```{r}
pp_check(mr.1)
```

---
## Create our own Posterior Predictive Distribution
50*118 = 5900
```{r}
MR %>% 
  select(-SES, -'intervention group') %>% 
 add_predicted_draws(mr.1) %>% 
    sample_draws(50) 
```


---

.pull-left[
```{r, eval = FALSE}
MR %>% 
  select(-SES, -'intervention group') %>% 
 add_predicted_draws(mr.1) %>% 
    sample_draws(50) %>% 
    ggplot(aes(.prediction, group = .draw)) +
   geom_line(stat = "density", alpha = .1) +
  geom_density(aes(happiness, group = .draw))+
  theme_classic()
```
]

.pull-right[
```{r, echo=FALSE}
MR %>% 
  select(-SES, -'intervention group') %>% 
 add_predicted_draws(mr.1) %>% 
    sample_draws(50) %>% 
    ggplot(aes(.prediction, group = .draw)) +
   geom_line(stat = "density", alpha = .1) +
  geom_density(aes(happiness, group = .draw))+
  theme_classic()
```
]

---

.pull-left[

The model’s epred/fitted against the observed data
```{r, message = FALSE, warning = FALSE, eval = FALSE}
MR %>% 
 add_epred_draws(mr.1) %>% 
  ggplot(aes(x = happiness , y = .epred)) +
  geom_abline(linetype = 2, color = "grey50", size = .5) +
  stat_interval(.width = c(.50, .95, .99)) +
  labs(y = "Predicted happiness")+
  xlim(0, 10) + ylim(0,10)
```
]

.pull-right[
Under predicts those high in happiness (maybe over predicts those low)
```{r, message = FALSE, warning = FALSE, echo = FALSE}
MR %>% 
 add_epred_draws(mr.1) %>% 
  ggplot(aes(x = happiness , y = .epred)) +
  geom_abline(linetype = 2, color = "grey50", size = .5) +
  stat_interval(.width = c(.50, .95, .99)) +
  labs(y = "Predicted happiness")+
  xlim(0, 10) + ylim(0,10)
```
]

---
## More than 2 groups

happiness ~ Normal( $\mu_i$ , $\sigma$ )  

$\mu_i$ = $\alpha_{\text{IV}[i]}$    

$\alpha_j$  ~ Normal(0, 5) , for j = 1,2,3   
$\sigma$  ~ Exponential(1) 


---

```{r}
mr.3 <- 
  brm(family = gaussian,
      happiness ~ 0 + iv,
      prior = c(prior(normal(5, 2), class = b),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = MR,
      sample_prior = T,
      file = "mr.3")

```

---

```{r}
prior.mr3<- prior_draws(mr.3)
prior.mr3
```



---
## prior distribution

.pull-left[
```{r, eval = FALSE}
prior.mr3 %>% 
  ggplot(aes(x = b)) +
  geom_density() +
  theme_bw() +
  theme(panel.grid = element_blank(),
        legend.position = c(.84, .84))
```
]

.pull-right[

```{r, echo = FALSE}
prior.mr3 %>% 
  ggplot(aes(x = b)) +
  geom_density() +
  theme_bw() +
  theme(panel.grid = element_blank(),
        legend.position = c(.84, .84))
```
]

---
```{r}
summary(mr.3)
```


---

```{r}
MR <- MR %>% 
  mutate(iv = factor(iv))
```

```{r}
mr.4 <- 
  brm(family = gaussian,
      happiness ~ 0 + iv,
      prior = c(prior(normal(5, 2), class = b),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = MR,
      sample_prior = T,
      file = "mr.4")

```

---


```{r}
summary(mr.4)
```


---

```{r}
get_variables(mr.4)
```

---

```{r}
mr.4 %>% 
 gather_draws(b_iv1, b_iv2,b_iv3) %>% 
    ggplot(aes(y = .variable, x = .value)) +
  stat_halfeye()
```


---
## 2+ categorical variables

```{r}
iv2 <- c("drug.a", "drug.b")

MR <- MR %>% 
  mutate(iv2 = sample(rep(iv2,  each = 59, size = n())))
         
 MR <- MR %>%         
         mutate(iv2 = factor(iv2))
```


---

```{r}
mr.5 <- 
  brm(family = gaussian,
      happiness ~ 0 + iv + iv2,
      prior = c(prior(normal(5, 2), class = b),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = MR,
      file = "mr.5")
```

---

```{r}
summary(mr.5)
```

---
## brms non-linear syntax
{brms} does not automatically create index variables for more than 1 categorical variable. The `0 + ` treats the first variable as an index but not the second, such that the second has a standard dummy interpretation.

Also, these tend to work better when the DV is centered or standardized. 

---
```{r}
MR <- MR %>% 
  mutate(happy_c = `happiness` - mean(`happiness`))

mr.6 <- 
  brm(family = gaussian,
      bf(happiness_c ~  a + b, # define 2 predictors
         a ~ 0 + iv, # specify the predictors
         b ~ 0 + iv2,
         nl = TRUE), # use non-linear syntax
      prior = c(prior(normal(0, 2), nlpar = a),
                prior(normal(0, 2), nlpar = b),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR,
      file = "mr.6")

```


---
```{r}
summary(mr.6)
```


---
```{r, message = FALSE}
MR %>%
  group_by(iv) %>%
  summarise(mean = mean(happy_c), n = n())
```


```{r, message = FALSE}
MR %>%
  group_by(iv2) %>%
  summarise(mean = mean(happy_c), n = n())
```

---

```{r}
get_variables(mr.6)
```

---

```{r}
mr.6 %>%
  gather_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  ggplot(aes(y = .variable, x = .value)) +
  stat_dotsinterval()

```

---

.pull-left[
```{r, eval = FALSE}
mr.6 %>%
  spread_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  mutate(iv1 = b_a_iv1 + 5.213902) %>% 
  mutate(iv2 = b_a_iv2 + 5.213902) %>% 
  mutate(iv3 = b_a_iv3 + 5.213902) %>% 
  gather_draws(iv1, iv2, iv3) %>% 
  ggplot(aes(y = .variable, x = .value)) +
  stat_dotsinterval()

```
]



.pull-right[
```{r, echo = FALSE}
mr.6 %>%
  spread_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  mutate(iv1 = b_a_iv1 + 5.213902) %>% 
  mutate(iv2 = b_a_iv2 + 5.213902) %>% 
  mutate(iv3 = b_a_iv3 + 5.213902) %>% 
  gather_draws(iv1, iv2, iv3) %>% 
  ggplot(aes(y = .variable, x = .value)) +
  stat_dotsinterval()

```
]

---
Krushke' visualization of posterior predictions 
```{r}
MR %>%
  data_grid(iv, .model = MR) %>%
  add_epred_draws(mr.6, dpar = c("mu", "sigma")) %>%
  sample_draws(50) %>%
  ggplot(aes(y = iv)) +
  stat_dist_slab(aes(dist = "norm", arg1 = mu, arg2 = sigma),
    slab_color = "gray65", alpha = 1/10, fill = NA) +
  geom_point(aes(x = happy_c), data = MR, shape = 21, fill = "#9ECAE1", size = 2)
```


---
## redundent predictors?

```{r}
pairs(mr.1)
```

---
## comparing levels ie contrasts

We could do this "by hand" or... 
```{r, eval = FALSE}
mr.6 %>%
  gather_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  compare_levels(.value, by = .variable) %>%
  ggplot(aes(y = .variable, x = .value)) +
  stat_halfeye()
```


---

```{r, echo = FALSE}
mr.6 %>%
  gather_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  compare_levels(.value, by = .variable) %>%
  ggplot(aes(y = .variable, x = .value)) +
  stat_halfeye()
```

---


```{r}
mr.6 %>%
  gather_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  compare_levels(.value, by = .variable) %>%
  group_by(.variable) %>%  
  mode_qi(.value)
```


---
## More complex contrasts? 
```{r}
mr.6 %>%
  spread_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  mutate(`12vs3` = (`b_a_iv1` + `b_a_iv2`)/2 - (`b_a_iv3`)) %>% 
  mean_qi(`12vs3`)
```

---
Or via helper functions
```{r}
hypothesis(mr.6, "(`a_iv1` + `a_iv2`)/2 - (`a_iv3`) = 0")
```

---
Or nice packages...?

```{r}
library(emmeans)
ref_grid(mr.6)
```

Which means index variables necessitate post hoc "by hand"

---
##  metric plus categorical
```{r}
mr.7 <- 
  brm(family = gaussian,
      bf(happy_c ~  a + b, 
         a ~ 0 + iv + SS_c, 
         b ~ 0 + iv2 + SS_c,
         nl = TRUE), # use non-linear syntax
      prior = c(prior(normal(0, 2), nlpar = a),
                prior(normal(0, 2), nlpar = b),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR,
      file = "mr.7")
```



---

```{r}
summary(mr.7)
```

---
```{r}
mr.8 <- 
  brm(family = gaussian,
      bf(happy_c ~  a + b + c, 
         a ~ 0 + iv , 
         b ~ 0 + iv2,
         c ~ 1 +  SS_c,
         nl = TRUE), # use non-linear syntax
      prior = c(prior(normal(0, 2), nlpar = a),
                prior(normal(0, 2), nlpar = b),
                prior(normal(0, 2), nlpar = c),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR,
      file = "mr.8")
```

---
```{r}
summary(mr.8)
```


```{r}
get_variables(mr.8)
```



---

```{r}
mr.9 <- 
  brm(family = gaussian,
      happy_c ~ 1 + iv + iv2 + SS_c, 
      prior = c(prior(normal(0, 5), class = Intercept),
                prior(normal(0, 2), class = b, coef = iv2),
                prior(normal(0, 2), class = b, coef = iv3),
                prior(normal(0, 2), class = b, coef = iv2drug.b),
                prior(normal(0, 2), class = b, coef = SS_c),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR,
      file = "mr.9")


```

---

```{r}
summary(mr.9)
```

---

```{r}
get_variables(mr.9)
```


---

```{r}
mr.8 %>%
  gather_draws(b_a_iv1, b_a_iv2, b_a_iv3) %>%
  compare_levels(.value, by = .variable) %>%
  group_by(.variable) %>%  
  median_qi(.value)
```

---

```{r}
library(emmeans)
emmeans(mr.9, specs = pairwise ~ iv)

```


---
```{r}
library(emmeans)
emmeans(mr.9, specs = pairwise ~ iv:iv2)

```



---

```{r}
mr.9 %>%
  emmeans( ~ iv | iv2) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = iv, y = .value)) +
  stat_eye() +
  facet_grid(~ iv2) 
```

---
## MLM preview
.pull-left[We can think of ANOVA models as MLM models with category as a random factor. Group-based deviations are reflected in the random effect of group $U_{0j}$. Our other two parameters are $\varepsilon_{ij}$ and $\gamma_{00}$ reflecting sigma and the mean of the group means, respectfully. 

Same for Bayes as for frequentest, nothing new]

.pull-right[

Level 1
$${Happy}_{ij} = \beta_{0j}  + \varepsilon_{ij}$$

Level 2
$${\beta}_{0j} = \gamma_{00} + U_{0j}$$


]

---

The unique part for Bayes is the introduction of a prior on the sd/random effect. The prior describes the distribution from which our groups arise and are centered around zero, meaning we need to think about the SD of the random effect. Random effects are not often thought of during normal experimental design considerations. Ie is the stimulus fixed vs random? See Judd, Westfall & Kenny 2012).

At this juncture we won't go into choosing values for the SD of the random effects. We have a few options such as creating "hyper" priors which learn from your data. 

If the SD is low, then deviations are thought to be zero, which will lead to large shrinkage. If high, deviations are not uncommon, and thus this more closely resembles ANOVA (with no shrinkage/learning from other groups)


---
```{r}

mr.10 <- 
  brm(family = gaussian,
      bf(happy_c ~  1 + (1|iv)),
          prior = c(prior(normal(0, 2), class = Intercept),
                prior(normal(0, 2), class = sd),
               prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR,
      file = "mr.10")

```

---
### MLM priors
SD represents the range of deviations of group means from the average
```{r, echo = FALSE, message=FALSE, warning=FALSE}
prior.mr10 <- c(prior(normal(0, 2), class = Intercept),
                prior(normal(0, 2), class = sd),
                prior(exponential(1), class = sigma))
prior.mr10 %>% 
  parse_dist(prior) %>% 
  ggplot(aes(y=class, dist =.dist, args=.args)) +
  stat_dist_halfeye()+
  scale_x_continuous( limits = c(-50, 50)) +
  labs(title="Priors")+ xlim(-10, 10)
```

---


```{r, warning=FALSE}
summary(mr.10)
```


---
## Population intercept
.pull-left[
```{r, echo= FALSE, warning=FALSE, message=FALSE}
library(ggridges)
MR %>% 
  group_by(iv) %>% 
  mutate(group_mean = mean(happy_c)) %>% 
  ungroup() %>% 
  mutate(iv = fct_reorder(iv, group_mean)) %>% 
  ggplot(aes(x = happy_c, y = iv, fill = factor(group_mean))) +
  geom_density_ridges(scale = 3/2, size = .2) 
```
]

.pull-right[

```{r, echo = FALSE, message = FALSE}

MR %>%
  group_by(iv) %>%
  summarise(mean = mean(happy_c)) %>% 
  summarise(mean = mean(mean))
```

]

---
## SD

```{r}
get_variables(mr.10)
```

```{r}
mr.10 %>%
  spread_draws(sd_iv__Intercept) %>% 
    mean_qi()
```

---

```{r, warning = FALSE, message = FALSE}
mr.10 %>%
  spread_draws(r_iv[group,])
```
4000 samples * 3 groups

---

Same info as before in the ANOVA framework (we just got fewer samples in mr.4 and that model used index coding)
```{r}
mr.4 %>% 
 gather_draws(b_iv1, b_iv2,b_iv3)
```

---
.pull-left[
```{r}
mr.10 %>%
  spread_draws(r_iv[group,]) %>% 
    mean_qi()
```
]

.pull-right[
```{r}
  MR %>%
  group_by(iv) %>%
  summarise(mean = mean(happy_c), n = n())

```
]


---

.pull-left[
```{r}
mr.4 %>% 
 gather_draws(b_iv1, b_iv2,b_iv3) %>% 
  ggplot(aes(y = .variable, x = .value)) +
  stat_dotsinterval()
  
```
]

.pull-right[
```{r, message = FALSE, warning = FALSE}
mr.10 %>%
  spread_draws(r_iv[group,]) %>% 
  mutate(group = as.factor(group)) %>% 
    ggplot(aes(y = group, x = r_iv)) +
  stat_dotsinterval() + xlim(-1,1)
```

]

---
## shrinkage and partial pooling

We get a) greater uncertainty and b) a greater push towards similar values across the groups. Why? 
(1) our regularizing (centered around zero) priors push mean to zero.   (2) we are partially pooling values across groups, shrinking the mean to the group mean.   

---
## shrinkage and partial pooling

(3) Incorporating uncertainty in the random effects. The SD parameter describes how large the differences between the groups is expected. Could groups differ by a 20, 30? Normally we expressed that through a prior around the regression coefficient. Here it is through a SD parameter. 

The model is taking the potential that they differ and placing that into the model as uncertainty. We said these differences "could happen" and the SD is only estimated with 3 groups, compared to a mean, so there is less evidence that .  

---
## Interactions

Continuing our translation of previous skills to a Bayesian framework. 

Interactions reflect when the influence of one variables depends on another. No longer can speak of main effects, now one needs to describe the association between two (or more) variables and the DV. The result is that the interpretation is the hard part, not necessarily the modeling. 

As models get more complex, interactions become more likely (anytime there is a boundary in the DV)


---
### Dichotomous example

```{r}

mr.11 <-
  brm(family = gaussian,
      happiness ~ 0 + iv.d + SS_c,
      prior = c(prior(normal(5, 3), class = b, coef = iv.dcontrol),
                prior(normal(5, 3), class = b, coef = iv.dtx),
                prior(normal(0, .5), class = b, coef = SS_c),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR, 
      file = "mr.11")
```

---
```{r}
summary(mr.11)
```

---
```{r}
MR %>%
  group_by(iv.d) %>%
  data_grid(SS_c = seq_range(SS_c, n = 50), .model = MR) %>%
  add_epred_draws(mr.11, ndraws = 100) %>%
  ggplot(aes(x = SS_c, y = happiness, color = iv.d)) +
  geom_line(aes(y = .epred, group = paste(iv.d, .draw)),alpha = .1) +
  geom_point(data = MR) 
```

---
### adding an interaction

```{r}
mr.12 <- 
  brm(family = gaussian,
      bf(happiness ~ 0 + a + b * SS_c, 
         a ~ 0 + iv.d, 
         b ~ 0 + iv.d,
         nl = TRUE),
      prior = c(prior(normal(5, 3), class = b, coef = iv.dcontrol, nlpar = a),
                prior(normal(5, 3), class = b, coef = iv.dtx, nlpar = a),
                prior(normal(0, .5), class = b, coef = iv.dcontrol, nlpar = b),
                prior(normal(0, .5), class = b, coef = iv.dtx, nlpar = b),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR, 
      file = "mr.12")
```


---
### get prior function

For those times you aren't sure what the priors should be or the names that go with them. Add: likelihood, model, and data. 
```{r}
get_prior(family = gaussian,
      bf(happiness ~ 0 + a + b * SS_c, 
         a ~ 0 + iv.d, 
         b ~ 0 + iv.d,
         nl = TRUE),
         data = MR)
```

---

```{r}
summary(mr.12)
```


---

```{r}
plot(mr.12)
```


---

```{r}
hypothesis(mr.12, "b_iv.dtx  < b_iv.dcontrol" )
```

---

```{r}
MR %>%
  group_by(iv.d) %>%
  data_grid(SS_c = seq_range(SS_c, n = 50), .model = MR) %>%
  add_epred_draws(mr.12, ndraws = 100) %>%
  ggplot(aes(x = SS_c, y = happiness, color = iv.d)) +
  geom_line(aes(y = .epred, group = paste(iv.d, .draw)),alpha = .1) +
  geom_point(data = MR) 
```

---

What if we fit it without index coding. "Normal"
```{r}
get_prior(family = gaussian,
      happiness ~ iv.d * SS_c,
         data = MR)
```



---
```{r}
mr.12a <- 
  brm(family = gaussian,
      happiness ~ iv.d * SS_c,
      prior = c(prior(normal(0, .5), class = b, coef = iv.dtx),
                prior(normal(0, .5), class = b, coef = SS_c),
                prior(normal(0, .5), class = b, coef = iv.dtx:SS_c),
                prior(normal(5, 3), class = Intercept),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      data = MR, 
      file = "mr.12a")
```


---

```{r}
summary(mr.12a)
```

---

```{r}
MR %>%
  group_by(iv.d) %>%
  data_grid(SS_c = seq_range(SS_c, n = 50), .model = MR) %>%
  add_epred_draws(mr.12a, ndraws = 100) %>%
  ggplot(aes(x = SS_c, y = happiness, color = iv.d)) +
  geom_line(aes(y = .epred, group = paste(iv.d, .draw)),alpha = .1) +
  geom_point(data = MR) 
```


---
```{r}
get_variables(mr.12a)
```



---
```{r}
mr.12a %>%
  spread_draws(`b_SS_c`, `b_iv.dtx:SS_c`) %>% 
  mutate(slope.c = `b_SS_c` ) %>%
  mutate(slope.tx = `b_SS_c` + `b_iv.dtx:SS_c`) %>% 
  gather_draws(slope.c, slope.tx) %>% 
  mean_qi() 
```


---
```{r, echo = FALSE}
mr.12a %>%
  spread_draws(`b_SS_c`, `b_iv.dtx:SS_c`) %>% 
  mutate(slope.c = `b_SS_c` ) %>%
  mutate(slope.tx = `b_SS_c` + `b_iv.dtx:SS_c`) %>% 
  gather_draws(slope.c, slope.tx) %>% 
  mean_qi() 
```

```{r}
mr.12 %>%
  gather_draws(b_b_iv.dcontrol, b_b_iv.dtx) %>% 
  mean_qi() 

```

---
## Continuous interaction example

```{r, echo = FALSE, message = FALSE}
Multipleregression  <- read_csv("Multipleregression.csv")

Multipleregression$Support.r <- (17.36 - Multipleregression$Support)/3

mr.model <- lm(Stress ~ Support.r + Anxiety, data = Multipleregression)
library(visreg)
visreg2d(mr.model,"Support.r", "Anxiety", plot.type = "persp")

```

---
```{r, echo = FALSE, message = FALSE}
Multipleregression  <- read_csv("Multipleregression.csv")

Multipleregression$Support.r <- (17.36 - Multipleregression$Support)/3

mr.model <- lm(Stress ~ Support.r* Anxiety, data = Multipleregression)
library(visreg)
visreg2d(mr.model,"Support.r", "Anxiety", plot.type = "persp")

```




---

```{r}
get_prior(family = gaussian,
      happiness ~ 1 + SS_c * FQ_c,data = MR)
```


---

```{r}
mr.13 <- 
  brm(family = gaussian,
      happiness ~ 1 + SS_c * FQ_c,
      prior = c(prior(normal(0, 3), class = Intercept),
                prior(normal(0, 2), class = b, coef = SS_c),
                prior(normal(0, 2), class = b, coef = FQ_c),
                prior(normal(0, 2), class = b, coef = SS_c:FQ_c),
                prior(exponential(1), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = MR,
      sample_prior = T,
      file = "mr.13")
```


---

```{r}
summary(mr.13)
```

---

```{r}
conditional_effects(mr.13, effects = "SS_c:FQ_c" )
```


---
## graphing


```{r}
library(psych)
describe(MR$FQ_c)
```



```{r}
MR %>% 
data_grid(SS_c = seq_range(SS_c, n = 20), FQ_c = c(-2.5,0,2.5), .model = MR) 

```

---

```{r}
MR %>% 
data_grid(SS_c = seq_range(SS_c, n = 20), FQ_c = c(-2.5,0,2.5), .model = MR) %>% add_epred_draws(mr.13)

```

---
.pull-left[
```{r, eval = FALSE}
MR %>% 
data_grid(SS_c = seq_range(SS_c, n = 20), FQ_c = c(-2.5,0,2.5), .model = MR) %>%
  add_epred_draws(mr.13) %>% 
  ggplot(aes(x = SS_c, y = happiness, group = FQ_c %>% as.character()))+
  stat_lineribbon(aes(y = .epred, color = FQ_c %>% as.character(), alpha = .05, fill = FQ_c ), .width = c(0.95),  show.legend = FALSE) +
  geom_point(data = MR) 

```
]

.pull-right[

```{r, echo = FALSE}
MR %>% 
data_grid(SS_c = seq_range(SS_c, n = 20), FQ_c = c(-2.5,0,2.5), .model = MR) %>%
  add_epred_draws(mr.13) %>% 
  ggplot(aes(x = SS_c, y = happiness, group = FQ_c %>% as.character()))+
  stat_lineribbon(aes(y = .epred, color = FQ_c %>% as.character(), alpha = .05, fill = FQ_c ), .width = c(0.95),  show.legend = FALSE) +
  geom_point(data = MR) 
```

]

---

.pull-left[
```{r, eval = FALSE}
MR %>% 
data_grid(SS_c = seq_range(SS_c, n = 20), FQ_c = c(-2.5,0,2.5), .model = MR) %>%
  add_epred_draws(mr.13, ndraws = 50)  %>%
  ggplot(aes(x = SS_c, y = happiness, group = interaction(SS_c, FQ_c), color = FQ_c %>%  as.character())) +
  geom_line(aes(y = .epred, group = paste(FQ_c, .draw), alpha = .5),show.legend = FALSE) +  
facet_grid(cols = vars(FQ_c))
```
]


.pull-right[
```{r, echo = FALSE}
MR %>% 
data_grid(SS_c = seq_range(SS_c, n = 20), FQ_c = c(-2.5,0,2.5), .model = MR) %>%
  add_epred_draws(mr.13, ndraws = 50)  %>%
  ggplot(aes(x = SS_c, y = happiness, group = interaction(SS_c, FQ_c), color = FQ_c %>%  as.character())) +
  geom_line(aes(y = .epred, group = paste(FQ_c, .draw), alpha = .5),show.legend = FALSE) +  
facet_grid(cols = vars(FQ_c))
```
]


---
## Factorial designs

When we have multiple categorical independent variables (and maybe some metric/continuous variables). 

Note that there are no SS derivations, no Fs -- because we don't use that type of estimation! But the logic is the same!

These are still linear models, so what are we doing different? 

---

```{r, message=FALSE, warning=FALSE}
anova <-read_csv("https://raw.githubusercontent.com/josh-jackson/bayes/master/anova.csv")
anova$SupportLevel<-cut(anova$Support, breaks = c(0,5,10,18), labels = c("low","med","high"))
anova <- anova %>% 
  mutate(group = as.factor(group))
```

If we want to fit a 3x2 ANOVA, what linear model are we running? 
```{r, eval = FALSE}
anxiety ~ group * SupportLevel
```


$$Y_{ijk} = b_{0} + b_{1}J1 + b_{2}K1 + b_{3}K2 + b_{4}J1:K1 + b_{5}J1:K2 +\varepsilon_{ijk}$$

---

3x2 Between subjects

|      |       |Group |           |     
|------|-------|------|------------|
|      |       | Tx   |  Control   |              
| Support   |low     |   |         |      
| Level     | med   |    |          |        
|           | high |    |           |  |


---

.tiny[
```{r}
get_prior(family = gaussian,
      Anxiety ~ group * SupportLevel,
      data = anova)
```
]



---

```{r}
mr.14 <- 
  brm(family = gaussian,
      Anxiety ~ group * SupportLevel,
      prior = c(prior(normal(5, 3), class = Intercept),
                prior(normal(0, 2), class = b, coef = groupTx),
                prior(normal(0, 2), class = b, coef =SupportLevelhigh),
                prior(normal(0, 2), class = b, coef = SupportLevelmed),
                prior(normal(0, 2), class = b, coef =groupTx:SupportLevelhigh),
                prior(normal(0, 2), class = b, coef = groupTx:SupportLevelmed),
                prior(student_t(3, 0, 2.5), class = sigma)),
      iter = 2000, warmup = 1000, chains = 2, cores = 2,
      data = anova,
      sample_prior = T,
      file = "mr.14")
```

---

```{r}
summary(mr.14)
```

---

How could we get posterior means for each group?

1. feed a matrix/compute longhand into equation to calculate group values for each of our 6 groups

```{r}
contrasts(anova$group)
```

```{r}
contrasts(anova$SupportLevel)
```

---

```{r}
mr.14 %>% 
  spread_draws(b_Intercept, b_groupTx, b_SupportLevelmed,b_SupportLevelhigh, `b_groupTx:SupportLevelmed`, `b_groupTx:SupportLevelhigh`) %>% 
  mutate(Con_Lo = b_Intercept + b_groupTx * 0 + b_SupportLevelmed * 0 + `b_SupportLevelhigh` * 0 * 0 + `b_groupTx:SupportLevelmed` *0 * 0 + `b_groupTx:SupportLevelhigh` *0 * 0,
         Con_Med = b_Intercept + b_groupTx * 0 + b_SupportLevelmed * 1 + b_SupportLevelhigh * 0 +  `b_groupTx:SupportLevelmed`*0 * 1 + `b_groupTx:SupportLevelhigh` *0 * 0,
         Con_Hi = b_Intercept + b_groupTx * 0 + b_SupportLevelmed * 0 + b_SupportLevelhigh *1 +  `b_groupTx:SupportLevelmed` *0 * 0+ `b_groupTx:SupportLevelhigh` *0 * 1)
```

---
How could we get posterior means for each group?

1. Feed a matrix/compute longhand into equation to calculate group values for each of our 6 groups

2. Feed similar info into the hypothesis function. This will be especially handy when we have LOTS of parameters from MLM models

---

hi vs medium in the control group
```{r}
hypothesis(mr.14, "Intercept + groupTx * 0 + SupportLevelmed * 1 + SupportLevelhigh * 0 +  `groupTx:SupportLevelmed`*0 * 1 + `groupTx:SupportLevelhigh` *0 * 0 > Intercept + groupTx * 0 + SupportLevelmed * 0 + SupportLevelhigh *1 +  `groupTx:SupportLevelmed` *0 * 0+ `groupTx:SupportLevelhigh` *0 * 1")
```

---

```{r}
mr.14 %>% 
  spread_draws(b_Intercept, b_groupTx, b_SupportLevelmed,b_SupportLevelhigh, `b_groupTx:SupportLevelmed`, `b_groupTx:SupportLevelhigh`) %>% 
  mutate(Con_Med = b_Intercept + b_groupTx * 0 + b_SupportLevelmed * 1 + b_SupportLevelhigh * 0 +  `b_groupTx:SupportLevelmed`*0 * 1 + `b_groupTx:SupportLevelhigh` *0 * 0,
         Con_Hi = b_Intercept + b_groupTx * 0 + b_SupportLevelmed * 0 + b_SupportLevelhigh *1 +  `b_groupTx:SupportLevelmed` *0 * 0+ `b_groupTx:SupportLevelhigh` *0 * 1, 
         hi_med_diff = Con_Hi - Con_Med) %>% 
  mean_qi(hi_med_diff)
```


---

How could we get posterior means for each group?

1. Feed a matrix/compute longhand into equation to calculate group values for each of our 6 groups

2. Feed similar info into the hypothesis function. This will be especially handy when we have LOTS of parameters from MLM models

3. Use a package that does this for you, like {emmeans}

---

```{r}
em.1<- emmeans(mr.14, c("group", "SupportLevel"))
em.1
```

---

```{r}
emmip(mr.14, group ~ SupportLevel)
```

---

```{r}
emmeans(mr.14, pairwise ~ SupportLevel)
```

---

```{r}
pairs(em.1)
```

---
But what if you want to graph? 

```{r, warning = FALSE, message = FALSE}
mr.14 %>%
  emmeans( ~ SupportLevel) %>%
  contrast(method = "pairwise") %>%
  gather_emmeans_draws() 
```

---

```{r, warning = FALSE, message = FALSE}
mr.14 %>%
  emmeans( ~ SupportLevel) %>%
  contrast(method = "pairwise") %>%
  gather_emmeans_draws() %>%
   ggplot(aes(x = .value, y = contrast)) +
  stat_halfeye()
```


---

```{r}

mr.14 %>%
  emmeans( ~ SupportLevel | group) %>%
  gather_emmeans_draws() %>%
   ggplot(aes(x = SupportLevel, y = .value, fill = group, color=group)) +
  stat_lineribbon(alpha = .4, .width = .99)
```

---

```{r}
mr.14 %>%
  emmeans( ~ SupportLevel | group) %>%
  gather_emmeans_draws() %>%
   ggplot(aes(x = SupportLevel, y = .value, fill = group, color=group)) +
  geom_line(aes(group = .draw), alpha = .005) +
  stat_pointinterval() +
  facet_grid(~ group) 
```


```{r}
mr.14 %>%
  emmeans( ~ SupportLevel | group) %>%
  gather_emmeans_draws() %>%
   ggplot(aes(x = SupportLevel, y = .value, fill = group, color=group)) +
  geom_line(aes(group = .draw), alpha = .005) +
  stat_pointinterval() +
  facet_grid(~ group) +
  geom_point(data = anova, aes(y = Anxiety))
```

